Q1 table

### 2021-11-04 Q1_table_characteristics_full.Rmd
S1 TABLE

#author column
Q1_table$study <- Q1_table$author_1
Q1_table$author_1 <- NULL
Q1_table$record_id <- NULL

@@

Q1_table <- Q1_table[, c(1, 4, 2, 3, 5, 6, 7, 8)]
```

@@

table1 %>% 
  as_flextable() %>% 
  set_header_labels(setting = "Setting",
                    location = "Location", 
                    year = "Year"
                    study = "Study",
                    total_SARS_n = "Total SARS-CoV-2, n",
                    asymp_SARS_n = "Asymptomatic SARS-CoV-2, n",
                    sex = "Sex of asymptomatic people",         
                    age = "Age of asymptomatic people, years, median",            
                    follow_up = "Follow-up method") %>%
  set_table_properties(layout = "autofit") %>%
  footnote(i = 1, j = 7,
           value = as_paragraph("Follow-up according to protocol (1: 14 days after last possible exposure; 2: 7 days after diagnosis; 3: until negative RT-PCR result; 4:>7 days after diagnosis). NR = not reported."),
           ref_symbols = "a",
           part = "header") #add footnote

>>>>

#author column
Q1_table$study <- paste(Q1_table$author_1, ", ", Q1_table$year, sep="")
Q1_table$author_1 <- NULL
Q1_table$year <- NULL
Q1_table$record_id <- NULL

@@

Q1_table <- Q1_table[, c(1, 3, 2, 4, 5, 6, 7, 8)]

@@

table1 %>% 
  as_flextable() %>% 
  set_header_labels(setting = "Setting",
                    location = "Location", 
                    study = "Study",
                    total_SARS_n = "Total SARS-CoV-2, n",
                    asymp_SARS_n = "Asymptomatic SARS-CoV-2, n",
                    sex = "Sex of asymptomatic people",         
                    age = "Age of asymptomatic people, years, median",            
                    follow_up = "Follow-up method") %>%
  set_table_properties(layout = "autofit") %>%
  footnote(i = 1, j = 7,
           value = as_paragraph("Follow-up according to protocol (1: 14 days after last possible exposure; 2: 7 days after diagnosis; 3: until negative RT-PCR result; 4:>7 days after diagnosis). NR = not reported."),
           ref_symbols = "a",
           part = "header") #add footnote
